### 2015-07-09 narrative/evaluation.tex
minor changes for readability.
spelling, etc.

\label{table:eval}
\centering
\begin{tabular}{ | p{1.4in} | p{2in} | p{2.5in} | }
  \hline
  {\bf Principle/Metric}                   & {\bf User perspective metric}   & {\bf System perspective metric }\\ \hline
  {\bf Knowledge-centric system}           & More knowledge = faster access to higher quality data &  More knowledge = better resource utilization across the entire hierarchy \\ \hline
  {\bf Predictable Performance Accuracy}   & More predictability = better quality of data &  Accuracy of the time bounds across multiple layers of the storage hierarchy wrote/read in time constrained situations\\ \hline
\end{tabular}

\caption{Guiding Principles}
\end{table}

@@

The first part of our evaluation will cover the following characteristics: (1)
the accuracy of time bounds estimates for applications when data is on just one
level of the storage hierarchy as well as when the data chunks are split; (2)
data discovery speed when chunks are spread across the hierarchy informing how
many pieces data can be split into before it takes too long to access most of
the data; and (3) how well we can migrate data and update our server to
determine if data might get out-of-sync between data chunks.  We will need to
clearly understand how well this system works on current systems and we will
need to investigate this on the next generation OLCF system (Summitt) and the
SNL system (Trinity) which we will have early access along with all of the
applications we will be investigating.

@@

The fourth part of the evaluation focuses on the additional user burden. One of
the risks in the proposed design is the unwillingness of users to add more
knowledge to the system. To better understand the user burden, we will attempt
to quantify the additional requirements to improve the automatic optimization.
We expect a substantial minimal burden to inform the automatic optimization.
Our evaluation will focus on the improvements gained through additional user
provided data and attempt to relate the pain/benefit tradeoff. The initial
hypothesis from working with many LCF users suggests that once the initial
burden to facilitate the automatic optimization, the additional burden required
to increase benefits is small enough to encourage users to participate more
heavily for greater benefit.

>>>>

\centering
\begin{tabular}{ | p{1.4in} | p{2in} | p{2.5in} | }
  \hline
  {\bf Principle/Metric}                   & {\bf User perspective metric}   & {\bf System perspective metric }\\ \hline
  {\bf Knowledge-centric system}           & More knowledge = faster access to higher quality data &  More knowledge = better resource utilization across the entire hierarchy \\ \hline
  {\bf Predictable Performance Accuracy}   & More predictability = better quality of data &  Accuracy of the time bounds across multiple layers of the storage hierarchy wrote/read in time constrained situations\\ \hline
\end{tabular}

\caption{Guiding Principles}
\label{table:eval}
\end{table}

@@

The first part of our evaluation will cover the following characteristics: (1)
the accuracy of time bounds estimates for applications when data is on just one
level of the storage hierarchy as well as when the data chunks are split; (2)
data discovery speed when chunks are spread across the hierarchy informing how
many pieces data can be split into before it takes too long to access most of
the data; and (3) how well we can migrate data and update our server to
determine if data might get out-of-sync between data chunks.  We will need to
clearly understand how well this system works on current systems and we will
need to investigate this on the next generation OLCF system (Summit) and the
SNL system (Trinity) which we will have early access along with all of the
applications we will be investigating.

@@

The fourth part of the evaluation focuses on the additional user burden. One of
the risks in the proposed design is the unwillingness of users to add more
knowledge to the system. To better understand the user burden, we will attempt
to quantify the additional requirements to improve the automatic optimization.
We expect a substantial minimal burden to inform the automatic optimization.
Our evaluation will focus on the improvements gained through additional user
provided data and attempt to relate the pain/benefit trade-off. The initial
hypothesis from working with many LCF users suggests that once the initial
burden to facilitate the automatic optimization, the additional burden required
to increase benefits is small enough to encourage users to participate more
heavily for greater benefit.
